---
title: "Homework 10"
author: "Anthony Ferraro"
output:
  html_document:
    code_folding: hide
    df_print: paged
linkcolor: blue
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, fig.align = "center", out.width = "50%", warning = FALSE, message = FALSE)

library(tidyverse)
library(knitr)
library(forcats)
library(ggplot2)
library(lubridate)

data("gss_cat")
data("lakers")

theme_set(theme_minimal())
```


#### Combining the Levels of the "Marital" Variable
```{r}
marital_gss_cat = gss_cat %>% mutate(
  marital = fct_collapse(marital,
                         "Pre-Marriage" = c("Never married"),
                         "Marriage" = c("Married"),
                         "Post-Marriage" = c("Separated", "Divorced", "Widowed"),
                         "Missing" = c("No answer")
                         )
  ) 

knitr::kable(marital_gss_cat %>% 
  count(marital))
```

^[Question 1 Complete]



#### Making a Column of the Proportion of Responses in a Year for Each Marriage Level
```{r}
year_marital_counts = marital_gss_cat %>%
  count(year, marital)

prop_marital_status = year_marital_counts %>%
  group_by(year) %>%
  mutate(prop = n / sum(n))
```

^[Question 2 Complete]




#### Re-Ordering the Levels of Marriage Status
```{r}
ordered_prop_marital = prop_marital_status %>%
  mutate(marital = fct_reorder2(marital, year, prop))
```

^[Question 3 Complete]




#### Making a Plot of Proportion vs. Year, Colored by Marriage
```{r}
ggplot(ordered_prop_marital, 
       aes(x = year, y = prop, color = marital)) +
  geom_line()
```

^[Question 4 Complete]




#### Trying to Convert the Date Integers to Actual Dates
```{r}
lakers %>%
  mutate(date_bad = as_date(date)) %>%
  select(date, date_bad) %>%
  head(n = 6) %>% knitr::kable()
```
I think this went wrong because R thinks that the date data provided is saying 20,081,028
days after 1970-01-01.

^[Question 5 Complete]




#### Converting Date to a String and Retrying
```{r}
lakers %>%
  mutate(date_str = as.character(date),
         date_good = ymd(date_str)) %>%
  select(date, date_str, date_good) %>%
  head(n = 6) %>% knitr::kable()
```

I think this worked because we converted the date column to string
data and then were able to use "ymd" to tell R what the layout of the
date data was.

^[Question 6 Complete]




#### Making a Bar Plot of Games on Each Day of the Week
```{r}
date_lakers = lakers %>%
  mutate(date_str = as.character(date),
         date_good = ymd(date_str))

date_lakers %>%
  distinct(date_good) %>%
  mutate(weekday = wday(date_good, label = TRUE)) %>%
  ggplot(aes(x = weekday)) +
  geom_bar()
```

^[Question 7 Complete]











